---
title: "HW3"
output: github_document
author: Xinyu Shen
---

##Problem 1

```{r}
library(tidyverse)
library(p8105.datasets)
data("instacart")

```

The dataset instacart has dimention of `r dim(instacart)[1]` X `r dim(instacart)[2]`. It has `r dim(instacart)[1]` variables, which are `r names(instacart)`. The key variables is the product_name, which help us to locate the product we want. The product_id variable can help us easily count how many such products were purchased, so it is important as well. For example, if the seller want to know how popular the spring water is, the seller can use the product name to locate the product and get its product id. Then the seller can count how many times this product id shows in the datasets, to know how popular the product is. 

```{r}
aisles_count = length(unique(pull(instacart, "aisle")))
df_most_item_aisle = instacart %>% group_by(aisle_id) %>% summarize(n=n()) 
most_item_aisle=max(df_most_item_aisle$n)
most_aisle_id = df_most_item_aisle$aisle_id[which(df_most_item_aisle$n==max(most_item_aisle))]
most_aisle_name = filter(instacart, aisle_id == most_aisle_id)[["aisle"]][1]
```

There are `r aisles_count` in the dataset, and `r most_aisle_name` is the most items ordered from. 

```{r}
df_item_aisles = instacart %>% group_by(aisle) %>% summarize(n=n()) 
item_plot = filter(df_item_aisles, n>10000) %>% mutate( 
  aisle= as.ordered(aisle)
  )
ggplot(item_plot, aes(x= aisle, y= n )) + geom_bar(stat = "identity")+ ylab("number in aisles") + coord_flip() +
  scale_x_discrete(limits = rev(levels(item_plot$aisle)))
```


```{r, message=FALSE, warning=FALSE}
df_three_most = instacart %>% filter(aisle %in% c("baking ingredients", "dog food care","packaged vegetables fruits")) %>% group_by(aisle, product_name) %>% summarize(num_times=n()) %>% arrange(-num_times, .by_group = TRUE) %>% top_n(3)
df_three_most
```
```{r}
df_p_c = instacart %>% filter(product_name %in% c('Pink Lady Apples', 'Coffee Ice Cream')) %>% select(product_name,order_dow, order_hour_of_day) %>% group_by(product_name, order_dow) %>% summarize(mean = mean(order_hour_of_day)) %>% pivot_wider(names_from = order_dow, values_from = mean) 
df_p_c
```

## Problem 2

```{r}
data("brfss_smart2010") 
df_ptwo = brfss_smart2010 %>% janitor::clean_names() %>% select("state" = locationabbr, "county" = locationdesc, everything()) %>% filter(topic == "Overall Health") %>% mutate(
  response = factor(response, levels = rev(unique(response)))
) %>% arrange(desc(response), .by_group = TRUE)

df_2002 = filter(df_ptwo, year == 2002) %>% group_by(state,county) %>% summarize(obs_n = n()) %>% select(state,county) %>% ungroup() %>% group_by(state) %>% summarize(n=n())%>% filter(n >= 7)
df_2010 = filter(df_ptwo, year == 2010) %>% group_by(state,county) %>% summarize(obs_n = n()) %>% select(state,county) %>% ungroup() %>% group_by(state) %>% summarize(n=n())%>% filter(n >= 7)
df_2002
df_2010
```

In 2002, `r df_2002[["state"]]` were observed 7 or more locations, and in 2010, `r df_2010[["state"]]` were observed 7 or more locations. Compared to 2002, more states have 7 or more location observed. 

```{r, warning=FALSE, message=FALSE}
df_pthree = df_ptwo %>% filter(response == "Excellent") %>% group_by(year, state) %>% summarize(data_mean = mean(data_value)) %>% ungroup()

ggplot(df_pthree, aes(x= year, y= data_mean)) + geom_line(aes(color = state))

```

Based on the plot, most states' data were ranged between 17.5 to 27.5, showing that the data were not changed significantly. 

```{r}
library(patchwork)
df_pthree_2006 = df_ptwo %>% filter(year == 2006 & state == "NY")
df_pthree_2010 = df_ptwo %>% filter(year == 2010 & state == "NY")
plot_06 = ggplot(df_pthree_2006, aes(x=response, y= data_value)) + geom_line(aes(color = county, group=county))+ggtitle("2006")
plot_10 = ggplot(df_pthree_2010, aes(x=response, y= data_value)) + geom_line(aes(color = county, group=county)) + ggtitle("2010")
plot_06 / plot_10
```

From the plot, we can see that better the response is, higher the data value. 

## Problem 3

```{r, warning=FALSE, message=FALSE}
df_acc = read_csv("./accel_data.csv") %>% janitor::clean_names() %>% pivot_longer(
  cols = starts_with("act") ,
  names_to = "visit",
  values_to = "activity_count") %>% mutate(
    wk_wek = ifelse(day == "Saturday" | day == "Sunday", "weekend", "weekday")
  )
df_acc
```
The dataset exits the variables such as `r names(df_acc)`, and has dimention of `r dim(df_acc)[1]` X `r dim(df_acc)[2]`, which contains `r nrow(df_acc)` observations. 

```{r}
week_order = c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
df_total_ac = df_acc %>% group_by(week, day) %>% summarize(sum = sum(activity_count)) %>% ungroup() %>% mutate(
  wd_wk = ifelse(day == "Saturday" | day == "Sunday", "weekend", "weekday"),
  day = factor(day, levels = week_order)
  )
df_total_ac
```


```{r}
ggplot(df_total_ac, aes(x=week, y = sum, fill = day)) + geom_bar(stat = 'identity', position = position_dodge())
```

From the plot, we can see that for the week 1,2 and 5, the activity total is increasing from Monday to Sunday. And in the week 3, Monday has significantly higher activity than other day and in week 4, Sunday has very low activity. And for week 4 and 5, in the Saturday, there is almost no activity for those two days. 

```{r}
df_acc2 = df_acc %>% mutate(
  visit = factor(substr(visit,10,1000), ordered = TRUE, levels = c(1:1440))
)
ggplot(df_acc2 %>% ungroup() %>% ungroup(), aes(x=factor(visit), y=activity_count, color = day)) +
  scale_x_discrete(breaks = seq(60,1440,60),labels = as.character(c(1:24))) +
  geom_line() +
  labs(title = "Activity account",
       x = "Hours",
       y = "Acitivity count") +
  theme(legend.position = "bottom")
```

From the plot, we can see that the activity peak shows between 19:00 to 22:00, which means the patient have most activity for a day. Also, we can see that in Sunday, the paitient prefer to move more between 11:00 and 12:00, and in Saturday, the paiteint prefer to move around 16:30. In Thursday, the paitient prefer to move at 7:00, which might be his weekly exercise time. In summary, the paitient move more during the weekdend, compared to the weekday. 

